The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-07 Writeup/paper_v3.tex
note about things to fix

%\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
%For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity. The figures show chi-squared and gamma functions fitted to the histogram \citep{Redshift_modelling}.
For our (flux-limited) sample of galaxies, up to $z=1.0(1.25)$, we fit
parametric models to the histograms of photometric redshifts in order
to assign values of overdensity.  We choose our bins to be $0.05$ wide
starting from $z=0.3$, where the bin width is selected to be somewhat
larger than the photometric redshift error but narrow enough that we
can still identify rather than averaging over real cosmological
structures.  We neglect the lowest
redshifts which have negligible cosmological volume and where the
galaxy population tends to be intrinsically bright and large enough
that a non-negligible fraction is lost due to the cuts we impose
(Sec.~\ref{S:data}).

>>>>

%\rachel{I thought we were only going up to $z=0.85$ but here you say $1$?}
%For our sample of galaxies, volume-limited upto $z=1$ by imposing an $M_I$ cut, we fit parametric models to the histogram of photometric redshifts in order to assign values of overdensity. The figures show chi-squared and gamma functions fitted to the histogram \citep{Redshift_modelling}.
For our (flux-limited) sample of galaxies, up to $z=1.0~(1.25)$
(\rachel{fix this to the correct one once we make final decisions}), we fit
parametric models to the histograms of photometric redshifts in order
to assign values of overdensity.  We choose our bins to be $0.05$ wide
starting from $z=0.3$, where the bin width is selected to be somewhat
larger than the photometric redshift error but narrow enough that we
can still identify rather than averaging over real cosmological
structures.  We neglect the lowest
redshifts which have negligible cosmological volume and where the
galaxy population tends to be intrinsically bright and large enough
that a non-negligible fraction is lost due to the cuts we impose
(Sec.~\ref{S:data}).
